\documentclass{article}

% packages
\usepackage{stix2}
\usepackage{geometry}
\geometry{
    letterpaper,
    margin=1.5in,
    centering,
    top=0.5in,
    bottom=0.3in, % small so \fancyfoot is close to bottom
    marginparwidth=0.7in,
    headsep=0.7in,
    footskip=1.0in,
    includehead,
    includefoot,
}
\renewcommand{\baselinestretch}{1.13}
\setlength{\parskip}{0.5\baselineskip}
\setlength{\parindent}{0pt}

\usepackage{titlesec}
\titleformat{\section}{\sffamily\LARGE\bfseries\center}{}{0em}{}{}

\usepackage{amsmath,amssymb}
\usepackage{tabularray}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{wasysym}
\usepackage[colorlinks=true,
            linkcolor=blue,
            filecolor=magenta,
            urlcolor=blue,
            bookmarksopen=true]{hyperref}
\usepackage[shortlabels]{enumitem}
% The following contains data specific to the course and semester:
\usepackage{fancyhdr} 
\fancyhead[L]{\textsf{CS 61-M1}}
\fancyhead[C]{\textbf{{\textsf{Discrete Math}}}}
\fancyhead[R]{\textsf{Fall~2024}}
\fancyfoot[L]{\textsf{\footnotesize\scriptsize{ }}}
\fancyfoot[C]{}
\fancyfoot[R]{\footnotesize\textsf{\copyright2024~Tufts~University}}


% commands
\NewDocumentCommand{\header}{ m O{Fall 2024}}{%
    \section{#1 \\ \normalsize\normalfont#2 \bigskip\bigskip
    }
}
\newcommand{\due}{\textbf{Due: }}
\newcommand{\hf}{\hspace*{\fill}}
\newcommand{\soln}[1]{ { % this extra brace contains the color command
    \color{red!90!black}#1}
}
\newcommand{\Part}[1]{\noindent\textbf{#1. \ }}
\newcommand{\thetextbook}{[Scheinerman, 3e]}
\newcommand{\tsec}[1]{\S\textbf{#1:}} % my formatting for textbook section number


\begin{document}
\pagestyle{fancy}
%\tableofcontents % Optional. You should get sidebar navigation links for your pdf reader even if you don't use this.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Some comments}
\textbf{\textcolor{red}{Please delete this section before you submit HW.}}

It is \textcolor{red}{NOT} required that you use this document, but hopefully you find it useful.
If you do use this file, put both \texttt{hw-01.tex} and \texttt{tex-shell.tex} in the same directory.
This document \texttt{tex-shell.tex} contains 
\begin{enumerate}
    \item   the ``preamble'' (with all the formatting commands and macro definitions)
            that goes \textit{before} the  \verb+\begin{document}+ 

    \item   \verb+\begin{document}+

    \item\label{mylabel}   \verb+\input{file}+ that inserts the contents of \texttt{file.tex} into this doc.   

    \item   \verb+\end{document}+
\end{enumerate}
When you pdflatex (or lualatex), you will get a \texttt{tex-shell.pdf}, so you would probably have to rename it.
Of course, next week just replace the \texttt{hw-01} with \texttt{hw-02} (I may or may not supply).

\subsection*{Design consideration:} You can have either 
\begin{enumerate}
    \item   Stand-alone hw-docs, each with their own preamble. 

            This gets rid of the \verb+\input{file}+ in step \ref{mylabel} above. 
            This might be easiest. 

    \item   A single global preamble. 

            This is what I do since when I change formatting or add 
            a macro definition the change is global across all my course docs.

            This also affords the possibility of  a single big doc that contains all 
            of your hw docs. 
\end{enumerate}
If you want one big doc that contains all of your hw docs, 
along with a table of contents, then 
\begin{enumerate}
   \item    leave the  \verb+\input{hw-01}+
   \item    uncomment the  \verb+\tableofcontents+

            This is optional. You should get sidebar navigation links for your pdf reader even if you don't use this.
   \item    uncomment the  \verb+\newpage\input{hw-02}+
   \item    You will have to pdflatex (or lualatex) twice for it to build the toc (or sidebar nav links, or label refs in the doc).

            The formatting is slightly different between pdflatex/lualatex for me, which I don't understand.
            Bonus point to anyone who explains that to me. \smiley
\end{enumerate}
But \textbf{PLEASE} submit only \textbf{one} \textbf{\texttt{hw-xy.pdf}} at a time to gradescope.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% the actual HW content gets input here:
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\input{hw-01}
% Next week, just replace the hw-01 with hw-02 (which I may or may not supply).

%\newpage
%\input{hw-02}

\end{document}

